R Notebook

### 2022-04-14 R/DeaminationAnalysis.rmd
Update DeaminationAnalysis.rmd

```{r setup_chunk}
library(knitr)
opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5)
if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}
```

@@

```{r plot_CPD_mismatch_type_frequency}
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotMismatchTypeFrequencies(CPDMismatchData[[i]][[j]],
                                title = paste("CPD", names(CPDMismatchData)[i], 
                                              names(CPDMismatchData[[i]])[j], "Mismatch Type Frequency"))
  }
}
```

```{r plot_6-4_mismatch_type_frequency}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotMismatchTypeFrequencies(sixFourMismatchData[[i]][[j]],
                                title = paste("6-4", names(sixFourMismatchData)[i], 
                                              names(sixFourMismatchData[[i]])[j], "Mismatch Type Frequency"))
  }
}

@@

```{r plot_CPD_mismatch_pos_frequency}
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste("CPD", names(CPDMismatchData)[i], 
                                                  names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"))
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste("CPD", names(CPDMismatchData)[i], 
                                                  names(CPDMismatchData[[i]])[j], "!C>T Mismatch Positions"))
  }
}
```

```{r plot_6-4_mismatch_pos_frequency}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste("6-4", names(sixFourMismatchData)[i], 
                                                  names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"))
    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste("6-4", names(sixFourMismatchData)[i], 
                                                  names(sixFourMismatchData[[i]])[j], "!C>T Mismatch Positions"))
  }
}

@@

```{r plot_CPD_tandem_C>T_pos_frequency}
for (i in 1:length(CPDTandemCTMismatches)) {
  for (j in 1:length(CPDTandemCTMismatches[[i]])) {
    plotMismatchPositionFrequencies(CPDTandemCTMismatches[[i]][[j]],
                                    title = paste("CPD", names(CPDTandemCTMismatches)[i], 
                                                  names(CPDTandemCTMismatches[[i]])[j], "Tandem C>T Mismatch Pos"))
  }
}
```

```{r plot_6-4_tandem_C>T_pos_frequency}
for (i in 1:length(sixFourTandemCTMismatches)) {
  for (j in 1:length(sixFourTandemCTMismatches[[i]])) {
    plotMismatchPositionFrequencies(sixFourTandemCTMismatches[[i]][[j]],
                                    title = paste("6-4", names(sixFourTandemCTMismatches)[i], 
                                                  names(sixFourTandemCTMismatches[[i]])[j], 
                                                  "Tandem C>T Mismatch Pos"))
  }
}
```

>>>>

```{r setup_chunk}
library(knitr)
opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, fig.path = "Deamination_Analysis_Figures/")
if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}
```

@@

```{r CPD_mismatch_type_frequency}
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotMismatchTypeFrequencies(CPDMismatchData[[i]][[j]],
                                title = paste("CPD", names(CPDMismatchData)[i], 
                                              names(CPDMismatchData[[i]])[j], "Mismatch Type Frequency"))
  }
}
```

```{r 6-4_mismatch_type_frequency}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotMismatchTypeFrequencies(sixFourMismatchData[[i]][[j]],
                                title = paste("6-4", names(sixFourMismatchData)[i], 
                                              names(sixFourMismatchData[[i]])[j], "Mismatch Type Frequency"))
  }
}

@@

```{r CPD_mismatch_pos_frequency}
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste("CPD", names(CPDMismatchData)[i], 
                                                  names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"))
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste("CPD", names(CPDMismatchData)[i], 
                                                  names(CPDMismatchData[[i]])[j], "!C>T Mismatch Positions"))
  }
}
```

```{r 6-4_mismatch_pos_frequency}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste("6-4", names(sixFourMismatchData)[i], 
                                                  names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"))
    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste("6-4", names(sixFourMismatchData)[i], 
                                                  names(sixFourMismatchData[[i]])[j], "!C>T Mismatch Positions"))
  }
}

@@

```{r CPD_tandem_C_to_T_pos_frequency}
for (i in 1:length(CPDTandemCTMismatches)) {
  for (j in 1:length(CPDTandemCTMismatches[[i]])) {
    plotMismatchPositionFrequencies(CPDTandemCTMismatches[[i]][[j]],
                                    title = paste("CPD", names(CPDTandemCTMismatches)[i], 
                                                  names(CPDTandemCTMismatches[[i]])[j], "Tandem C>T Mismatch Pos"))
  }
}
```

```{r 6-4_tandem_C_to_T_pos_frequency}
for (i in 1:length(sixFourTandemCTMismatches)) {
  for (j in 1:length(sixFourTandemCTMismatches[[i]])) {
    plotMismatchPositionFrequencies(sixFourTandemCTMismatches[[i]][[j]],
                                    title = paste("6-4", names(sixFourTandemCTMismatches)[i], 
                                                  names(sixFourTandemCTMismatches[[i]])[j], 
                                                  "Tandem C>T Mismatch Pos"))
  }
}
```

```{r Facet_Mismatch_Position_Frequencies, fig.width = 9, fig.height = 5}
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
                                         title = "CPD C>T Mismatch Pos Freq Rep1")
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
                                         title = "CPD C>T Mismatch Pos Freq Rep2")
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
                                         title = "6-4 C>T Mismatch Pos Freq Rep1")
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
                                         title = "6-4 C>T Mismatch Pos Freq Rep2")
```
